---
title: "fb2_border_collies"
author: "Lucrezia Lonardo"
date: "03/11/2020"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(readr)
library(ggsignif)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")

```

## loading data

```{r}

border_data <-read_csv("~/R/fb_dogs/data/fb2_bc.csv")%>%
  mutate(correct=as.numeric(ifelse(choice=="baited",0,ifelse(choice=="empty",1,""))))%>%
  mutate(fci_group = as.factor(fci_group))%>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))
summary(border_data)
str(border_data)

#view(dfSummary(fb_data))

```

```
## Plotting choice

```{r}
plot.data <- border_data %>%
  group_by(condition)%>%
  summarise(mean.correct=mean(correct), sd.correct=sd(correct), sum.correct=sum(correct), median.correct=median(correct), n.correct=length(correct), se.correct=sd(correct)/sqrt(length(correct)))
plot.data

p.choice<-ggplot(
  data=plot.data, aes(x=condition, y=mean.correct)) +
  geom_bar(stat="identity", alpha=0.5)+
  geom_errorbar(aes(ymin=mean.correct-se.correct, ymax=mean.correct+se.correct), width=.2) +
  ylim(0,0.8)+
  #geom_signif(comparisons=list(c("False Belief", #"True Belief")), annotations="*",
 #             y_position = 0.75, tip_length = 0.07, #vjust=0.4) +
  theme_classic()+
  labs(x="Group",y="Proportion of bucket A choices")+
  ggtitle("Border Collies")
 p.choice
 
#saving the plot with ggsave
ggsave(
  "bucket_A_choices_BC.png",
  plot = last_plot(),
  device = NULL,
  path = "C:/Users/lonardol/Desktop/False Belief experiment/FB_2_follow_up/Graphs/Border Collies",
  scale = 0.8,
  width = 5,
  height = 6,
  units = c("in", "cm", "mm"),
  dpi = 320,
  limitsize = TRUE
)
```
analysing the effect of group on condition: generalised linear mixed model

```{r}
model.data <- border_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(sex), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(condition), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(first_baited_box), scale=F, center=T)))
         
as.data.frame(model.data)


xx.fe.re=fe.re.tab(fe.model="correct ~ condition + age + sex + first_baited_box",
                   re="(1|breed)", data=border_data)
xx.fe.re$summary

## code to run the model
full.choice.breed <- glm(correct ~ condition + z.age + sex + first_baited_box, 
             data = model.data, family = binomial, 
)
```
#coefficients (estimate and std. error )
```{r}
round(summary(full.choice.breed)$coefficients, 3)
```
#chisq. (LRT) and p
```{r}
drop1.full=drop1(full.choice.breed, test="Chisq")
round(drop1.full,3)
```

```{r}
summary(full.choice.breed)$varcor
```

```


```

```



