---
title: "False Belief Task 2020"
author: ""
date: "July 22, 2020"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(glmmTMB)
#library(sjPlot)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")


#install.packages("")

#load(file ="mm1_mult_poss.RData")



```

```{r loading data, include = FALSE}
fb_data <- read.csv(file="data/20200721_lucrezia_false_belief_task_data.csv")%>%
  mutate(correct=as.numeric(ifelse(choice=="baited",1,ifelse(choice=="empty",0,""))))%>%
  mutate(fci_group = as.factor(fci_group))%>%
  mutate(id= 1:length(dog))%>%
  filter(dog!="Luna22" & dog!="Luna25")%>%
  droplevels()
summary(fb_data)

hist(fb_data$latency)

#view(dfSummary(fb_data))

```

### GLMM


#GLMM with parker group as random intercept

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="latency ~ condition + age + sex + first_baited_box",
                   re="(1|parker_group)+(1|communicator)", data=fb_data)
xx.fe.re$summary
```



``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- fb_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(sex), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(condition), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(first_baited_box), scale=F, center=T)))

as.data.frame(model.data)
#view(dfSummary(model.data))
```

``` {r mixed modeling, error=TRUE}

## code to run the model
full.latency <- glmmTMB(latency ~ condition + z.age + sex + first_baited_box+
             (1+condition.c + z.age + sex.c + first_baited_box.c || parker_group) + (1+condition.c + z.age + sex.c + first_baited_box.c || communicator), 
             data = model.data, 
             family=Gamma(link="log"), control=glmmTMBControl(optCtrl=list(iter.max=1000000000, eval.max=1000000000))
)

```


#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.full <- lm(latency ~ condition + z.age + sex + first_baited_box, data = model.data)
vif(col.full)
#no problem
```


####Model output
  + Coefficients
```{r}
summary(full.latency)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.latency, test="Chisq")
round(drop1.full,3)
```


### Model with breed as random intercept


```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="latency ~ condition + age + sex + first_baited_box",
                   re="(1|breed)+(1|communicator)", data=fb_data)
xx.fe.re$summary
```

``` {r mixed modeling, error=TRUE}

## code to run the model
full.latency.breed <- glmmTMB(latency ~ condition + z.age + sex + first_baited_box+
             (1+condition.c +  sex.c + first_baited_box.c || breed) + (1+condition.c + z.age + sex.c + first_baited_box.c || communicator), 
             data = model.data, 
             family=Gamma(link="log"), control=glmmTMBControl(optCtrl=list(iter.max=1000000000, eval.max=1000000000))
)
```


####Model output
  + Coefficients
```{r}
summary(full.latency.breed)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.latency.breed, test="Chisq")
round(drop1.full,3)
```







