---
title: "False Belief Task 2020"
author: ""
date: "July 22, 2020"
output:
  pdf_document: default
  html_document: default
---


#### test

test



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
#library(sjPlot)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")


#install.packages("")

#load(file ="mm1_mult_poss.RData")



```

```{r loading data, include = FALSE}
fb_data <- read.csv(file="data/20200721_lucrezia_false_belief_task_data.csv")%>%
  mutate(correct=as.numeric(ifelse(choice=="baited",1,ifelse(choice=="empty",0,""))))%>%
  mutate(fci_group = as.factor(fci_group))%>%
  mutate(id= 1:length(dog))%>%
  filter(dog!="Luna22" & dog!="Luna25")%>%
  rename("first_trial_fam"="first_trial_fam..1.yes..followed.communicator.")%>%
  droplevels()
summary(fb_data)


#view(dfSummary(fb_data))

```

### first trial of familiarisation correct
```{r}
binom.test(x=sum(fb_data$first_trial_fam), n=length(fb_data$first_trial_fam), p=0.5, alternative="two.sided")
```



#### Plotting the choices

```{r}

plot.data <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))%>% #renaming of factor levels
  mutate(correct=as.numeric(ifelse(choice=="baited",1,ifelse(choice=="empty",0,""))))%>%
  group_by(condition)%>%
  summarise(mean.correct=mean(correct), sd.correct=sd(correct), sum.correct=sum(correct), median.correct=median(correct), n.correct=length(correct), se.correct=sd(correct)/sqrt(length(correct)))


p.choice<-ggplot(
  data=plot.data, aes(x=condition, y=mean.correct)) +
  geom_bar(stat="identity", alpha=0.5)+
  geom_errorbar(aes(ymin=mean.correct-se.correct, ymax=mean.correct+se.correct), width=.2) +
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="Proportion of baited bucket choices")+
  ggtitle("Choice performance")
  
 
```


### Plotting latencies
```{r}

plot.data.latency <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))#renaming of factor levels

p.latency<-ggplot(
  data=plot.data.latency, aes(x=condition, y=log(latency))) +
  geom_boxplot(alpha=0.5)+
  theme_classic()+
  labs(x="Condition",y="Latency (log transformed)")+
  ggtitle("Latency")
 
```

```{r}
combined_plots<-plot_grid(p.choice, p.latency, nrow=1, labels=c("A", "B"))
combined_plots
ggsave(plot=combined_plots,filename = "graphs/choice and latency.png", units = "cm", width = 8, height = 5, dpi= 600, scale = 1.7)
```

### Anticipatory looking

### Plotting latencies
```{r}

plot.data.ant <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))%>%#renaming of factor levels
  group_by(condition)%>%
  add_count(prop_lt_baited_pause)


p.ant.fb<-ggplot(
  data=plot.data.ant%>%filter(condition=="False Belief"), aes()) +
 # geom_boxplot(aes(x=1, y=prop_lt_baited_pause), alpha=0.5)+
  #geom_boxplot(aes(x=2, y=prop_lt_empty_pause), alpha=0.5)+
  geom_jitter(data=plot.data.ant%>%filter(condition=="False Belief"),aes(x="baited", y=prop_lt_baited_pause),  colour = "darkgrey", alpha=0.4, width = 0.25) +
  geom_jitter(data=plot.data.ant%>%filter(condition=="False Belief"), aes(x="empty", y=prop_lt_empty_pause),  colour = "darkgrey", alpha=0.4, width = 0.25) +
  geom_boxplot(data=plot.data.ant%>%filter(condition=="False Belief" & prop_lt_baited_pause>0), aes(x="baited", y=prop_lt_baited_pause), alpha=0.5)+
  geom_boxplot(data=plot.data.ant%>%filter(condition=="False Belief" & prop_lt_empty_pause>0), aes(x="empty", y=prop_lt_empty_pause), alpha=0.5)+
  theme_classic()+
  labs(x="Condition",y="")
 

p.ant.tb<-ggplot(
  data=plot.data.ant%>%filter(condition=="True Belief"), aes()) +
 # geom_boxplot(aes(x=1, y=prop_lt_baited_pause), alpha=0.5)+
  #geom_boxplot(aes(x=2, y=prop_lt_empty_pause), alpha=0.5)+
  geom_jitter(data=plot.data.ant%>%filter(condition=="True Belief"),aes(x="baited", y=prop_lt_baited_pause),  colour = "darkgrey", alpha=0.4, width = 0.25) +
  geom_jitter(data=plot.data.ant%>%filter(condition=="True Belief"), aes(x="empty", y=prop_lt_empty_pause),  colour = "darkgrey", alpha=0.4, width = 0.25) +
  geom_boxplot(data=plot.data.ant%>%filter(condition=="True Belief" & prop_lt_baited_pause>0), aes(x="baited", y=prop_lt_baited_pause), alpha=0.5)+
  geom_boxplot(data=plot.data.ant%>%filter(condition=="True Belief" & prop_lt_empty_pause>0), aes(x="empty", y=prop_lt_empty_pause), alpha=0.5)+
  theme_classic()+
  labs(x="Condition",y="")

plot_grid(p.ant.fb, p.ant.tb, labels=c("FB", "TB"))
```
```{r}


plot.data.ant2 <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))%>%#renaming of factor levels
  mutate(prop_lt_buckets=prop_lt_baited_pause+prop_lt_empty_pause, prop_lt_empty_buckets = prop_lt_empty_pause/(prop_lt_baited_pause+prop_lt_empty_pause)) 


p.ant.con2_wo_zeros<-ggplot(
  data=plot.data.ant2%>%filter(prop_lt_buckets>0), aes(x=condition, prop_lt_buckets)) +
  geom_boxplot(alpha=0.5, outlier.colour="white")+
  geom_jitter( colour = "darkgrey", alpha=0.4, width = 0.25) +
  theme_classic()+
  labs(x="Condition",y="")


p.ant.con2<-ggplot(
  data=plot.data.ant2, aes(x=condition, prop_lt_buckets)) +
  geom_boxplot(alpha=0.5, outlier.colour="white")+
  geom_jitter( colour = "darkgrey", alpha=0.4, width = 0.25) +
  theme_classic()+
  labs(x="Condition",y="")


p.ant.con3<-ggplot(
  data=plot.data.ant2, aes(x=condition, prop_lt_empty_buckets)) +
  geom_boxplot(alpha=0.5, outlier.colour="white")+
  geom_jitter( colour = "darkgrey", alpha=0.4, width = 0.25) +
  theme_classic()+
  labs(x="Condition",y="")

plot_grid(p.ant.con2_wo_zeros, p.ant.con2,p.ant.con3,nrow=1, labels=c("A", "B", "C"))
```


### GLMM


#GLMM with parker group as random intercept

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ condition + age + sex + first_baited_box",
                   re="(1|parker_group)+(1|communicator)", data=fb_data)
xx.fe.re$summary
```



``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- fb_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(sex), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(condition), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(first_baited_box), scale=F, center=T)))

as.data.frame(model.data)
#view(dfSummary(model.data))
```

``` {r mixed modeling, error=TRUE}

## code to run the model
full.choice <- glmer(correct ~ condition + z.age + sex + first_baited_box+
             (1+condition.c + z.age + sex.c + first_baited_box.c || parker_group) + (1+condition.c + z.age + sex.c + first_baited_box.c || communicator), 
             data = model.data, family = binomial, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.full <- lm(correct ~ condition + z.age + sex + first_baited_box, data = model.data)
vif(col.full)
#no problem
```


####Model output
  + Coefficients
```{r}
round(summary(full.choice)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.choice, test="Chisq")
round(drop1.full,3)
```


```{r}
full.choice.glm <- glm(correct ~ condition + z.age + sex + first_baited_box, 
             data = model.data, family = binomial)

summary(full.choice.glm)
drop1(full.choice.glm, test="Chisq")
```



### Model with breed as random intercept


```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ condition + age + sex + first_baited_box",
                   re="(1|breed)+(1|communicator)", data=fb_data)
xx.fe.re$summary
```

``` {r mixed modeling, error=TRUE}

## code to run the model
full.choice.breed <- glmer(correct ~ condition + z.age + sex + first_baited_box+
             (1+ sex.c + condition.c + first_baited_box.c || breed)+(1+ z.age+ sex.c + condition.c + first_baited_box.c || communicator), 
             data = model.data, family = binomial, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Model output
  + Coefficients
```{r}
round(summary(full.choice.breed)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.choice.breed, test="Chisq")
round(drop1.full,3)
```







